\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{array}
\usepackage{titlesec}
\usepackage{ragged2e}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=0.18em, topsep=0.3em}
\definecolor{heading}{HTML}{123A56}
\definecolor{textbody}{HTML}{222222}
\definecolor{muted}{HTML}{5F6B76}

\titleformat{\section}{\large\bfseries\color{heading}}{}{0em}{}[\vspace{0.25em}\titlerule]
\titlespacing*{\section}{0pt}{0.9em}{0.45em}

\newcommand{\resumeheader}[1]{{\fontsize{20}{24}\selectfont\bfseries\color{heading} #1}}
\newcommand{\contact}[1]{{\small\color{muted} #1}}
\newcommand{\entry}[4]{
  \vspace{0.25em}
  \begin{tabularx}{\textwidth}{@{}X>{\raggedleft\arraybackslash}p{2.35in}@{}}
    {\bfseries #1} & {\small\color{muted} #2} \\
    {\itshape #3} & {\small\color{muted} #4} \\
  \end{tabularx}\vspace{0.1em}
}

\begin{document}
\color{textbody}

\resumeheader{Vijay Mathew}

\vspace{0.25em}
\contact{Bangalore, India \quad | \quad +91 7558892622 \quad | \quad \href{mailto:mathew.vijay@gmail.com}{mathew.vijay@gmail.com}}

\contact{\href{http://schemer.in}{schemer.in} \quad | \quad \href{https://github.com/vijaymathew/}{github.com/vijaymathew}}

\section*{Professional Summary}
Software architect and hands-on engineer with 20+ years of experience building programming languages, distributed services, developer platforms, search systems, and embedded software. Strong background in Clojure, Java, Scheme, C/C++, and Python, with a track record of leading architecture, shipping production systems at scale, and solving hard systems problems as both an individual contributor and a technical leader.

\section*{Core Strengths}
\begin{itemize}
  \item Distributed systems, service architecture, language design, developer tooling, search and content platforms
  \item Technical leadership, greenfield design, production delivery, performance-sensitive systems, remote collaboration
  \item Languages and tools: TypeScript, Clojure, Java, Scheme, C, C++, Python, PostgreSQL, MySQL
\end{itemize}

\section*{Professional Experience}

\entry{Fractl}{Apr 2018 -- Present}{Founding Engineer and Software Architect}{Bangalore}
\begin{itemize}
  \item Leading the design of a declarative language and runtime for domain modeling at \href{https://www.fractl.io/}{fractl.io}.
  \item Shaping core language abstractions, execution model, and developer-facing architecture for the platform.
\end{itemize}

\entry{SAP Concur}{Dec 2014 -- Apr 2018}{Principal Engineer}{Bangalore}
\begin{itemize}
  \item Led the design and implementation of a scalable identity management and authorization service.
  \item Built and brought the service to production as the primary engineer; it served 40+ million requests per day at launch.
  \item Stack: Clojure, Java, Python, MySQL, Elasticsearch, Couchbase.
\end{itemize}

\entry{HappiestMinds}{Jun 2012 -- Dec 2014}{Senior Technical Lead}{Bangalore}
\begin{itemize}
  \item Designed and built content indexing, search, and delivery services for Pearson Education's next-generation EPUB reader.
  \item Implemented the Python SDK for authentication services.
  \item Stack: Java, Spring REST, Python, Elasticsearch.
\end{itemize}

\entry{Actiance}{Apr 2007 -- Jun 2012}{Senior Systems Analyst}{Bangalore}
\begin{itemize}
  \item Designed the information leak prevention subsystem for an enterprise network monitoring platform, including content classification and in-stream policy enforcement.
  \item Built an RPC framework based on Google Protocol Buffers for efficient transport of captured IM/UC content.
  \item Delivered network auditing tools and integrations across IBM Sametime, Microsoft SharePoint, and Microsoft OCS; also built a Flex-based visualization tool for communication pattern analysis.
\end{itemize}

\entry{SpikeSource}{Aug 2006 -- Apr 2007}{Senior Software Engineer}{Bangalore}
\begin{itemize}
  \item Contributed to Stargate, a build and integration platform, using Java, C++, and Python.
\end{itemize}

\entry{Mindteck}{Mar 2006 -- Aug 2006}{Senior Software Engineer}{Bangalore}
\begin{itemize}
  \item Developed embedded software in C and C++ for chromatographic device control systems.
\end{itemize}

\entry{Fischer Systems}{Feb 2004 -- Feb 2006}{Software Engineer}{Trivandrum}
\begin{itemize}
  \item Built synchronization products and integration tooling including a BlackBerry Java application, a generic synchronization platform, an LDAP ODBC driver, and Outlook, Lotus Notes, and GroupWise connectors.
  \item Developed server-side and desktop components in C++, PHP, JavaScript, and Java Swing.
\end{itemize}

\entry{DArts}{May 2003 -- Jan 2004}{Software Engineer}{Tiruvalla}
\begin{itemize}
  \item Designed and implemented an Internet kiosk management system in C++ and delivered bespoke web applications on the LAMP stack.
\end{itemize}

\entry{Indusware Solutions}{Feb 2001 -- May 2003}{Software Engineer}{Tiruvalla}
\begin{itemize}
  \item Developed end-user products including Planet Zip, Planet Split, and IChat across Delphi, C++, and Java.
\end{itemize}

\entry{Freelance Consultant}{Jan 2000 -- Feb 2001}{Software Engineer}{Kozhencherry}
\begin{itemize}
  \item Built and marketed a complete software solution for private banks, including GUI and datastore components, in Visual C++.
\end{itemize}

\section*{Open Source Projects}
\entry{Nex}{Ongoing}{Creator}{}
\begin{itemize}
  \item \href{https://github.com/vijaymathew/nex}{github.com/vijaymathew/nex} --- Practical, expression-oriented programming language focused on clear control flow, contracts, classes, and teachable software engineering discipline.
\end{itemize}

\entry{Slogan}{2018}{Creator}{}
\begin{itemize}
  \item \href{http://schemer.in/slogan}{schemer.in/slogan} --- High-level dynamic programming language that compiles to efficient machine code and supports parallel execution.
\end{itemize}

\entry{Reo}{2020}{Contributor}{}
\begin{itemize}
  \item \href{https://github.com/anvetsu/reo}{github.com/anvetsu/reo} --- Programming language and environment for data analysis.
\end{itemize}

\section*{Technical Publications \& Writings}
\entry{The Document is the Computer}{2026}{Author}{}
\begin{itemize}
  \item \href{https://vijaymathew.github.io/books/ui/the-document-is-the-computer.html}{The Document is the Computer} --- Architectural manuscript proposing a text-native interface for personal computing, dissolving the "app" paradigm in favor of composable, document-based systems.
\end{itemize}

\entry{Supercharge Your CLI}{2025}{Author}{}
\begin{itemize}
  \item \href{https://vijaymathew.github.io/books/cli/html/index.html}{Supercharge Your CLI} --- A workflow playbook for high-performance command-line habits, focusing on composability and production-ready terminal environments.
\end{itemize}

\entry{Beyond Code / Programming with Nex}{2026}{Author}{}
\begin{itemize}
  \item \href{https://vijaymathew.github.io/nex/docs/beyond-code/index.html}{Beyond Code} --- A series of books and guided tutorials teaching software engineering discipline, grounded in the Nex programming language.
\end{itemize}

\section*{Education}
\entry{Mahatma Gandhi University}{Apr 1995 -- Apr 1998}{Bachelor's Degree}{Kottayam}
Major: Financial Accounting with Cost Accounting and Statistics.

\end{document}
